Coherent IR-Hyper-Raman Four Wave Mixing Vibrational Spectroscopy

### 2024-07-29 paper.tex
small issue in abstract

\begin{abstract}
Nonlinear, four wave mixing vibrational spectroscopies are often used to probe intramolecular vibrational coupling and relaxation dynamics in isotropic media.
Most of these methods rely on infrared and/or Raman transitions, such as sum-frequency generation (SFG) spectroscopy, but methods involving hyper-Raman transitions are also possible. 
The additional number of tensor elements in the hyper-Raman hyperpolarizability have been useful for probing condensed phase media. 
Implementing a nonlinear spectroscopy involving hyper-Raman transitions can provide a useful analogue to infrared and Raman based nonlinear spectroscopies to understand the spectroscopy and dynamics of isotropic systems.
Hyper Difference Frequency Generation (Hyper-DFG, or HDFG) spectroscopy is an underdeveloped four wave mixing vibrational spectroscopy based on the hyper-Raman transition. 
Despite several experimental reports on HDFG, its spectroscopic properties have not been fully explored.  
To this end, we investigate the selection rules and behavior of HDFG spectroscopy as an upconverted infrared spectroscopy and as a probe of vibronic coupling in molecular systems.
HDFG shows promise as a method to disentangle vibrational spectra and dynamics in isotropic systems.

>>>>

\begin{abstract}
Nonlinear, four wave mixing vibrational spectroscopies are often used to probe intramolecular vibrational coupling and relaxation dynamics in isotropic media.
Most of these methods rely on infrared and/or Raman transitions but methods involving hyper-Raman transitions are also possible. 
Implementing a nonlinear spectroscopy involving hyper-Raman transitions can provide a useful analogue to infrared and Raman based nonlinear spectroscopies to understand the spectroscopy and dynamics of isotropic systems.
Hyper Difference Frequency Generation (Hyper-DFG, or HDFG) spectroscopy is an underdeveloped four wave mixing vibrational spectroscopy based on the hyper-Raman transition. 
The method is similar in implementation to that of vibrational sum frequency generation (vSFG) and difference frequency generation (vDFG) spectroscopy.
Despite several experimental reports on HDFG, its spectroscopic properties have not been fully explored.  
To this end, we investigate the selection rules and behavior of HDFG spectroscopy as an upconverted infrared spectroscopy and as a probe of vibronic coupling in molecular systems.
HDFG shows promise as a method to disentangle vibrational spectra and dynamics in isotropic systems.
